Is high social class always beneficial for survival? A study of northern Sweden 1801--2013

### 2018-09-27 marginal.Rmd
what?

```{r cumswtab, message=FALSE, cache = TRUE, eval = TRUE}
fitt <- coxph(Surv(enter, exit, event) ~ hisclass * period * sex + civst + urban, data = vb1)

# vb3064$social_class <- vb3064$hisclass
# vb3064$marital_status <- vb3064$civst
# vb3064$urban_or_rural <- vb3064$urban
# vb3064$age_group <- vb3064$age
# fitt <- glm(event ~ offset(log(exposure)) + urban_or_rural + marital_status + age_group + sex * social_class * period,
#             data = vb3064, family = poisson)
dr <- drop1(fitt, test = "Chisq")
# ##dr
knitr::kable(dr, caption = "Single term deletions, ages 30-64.")
# ##print(xtable(dr,label = "tab:cumswtab", caption = "Mortality: ANOVA, ages 30--64."),
  ##    type = "latex", comment = FALSE)
```

>>>>

```{r cumswtab, message=FALSE, cache = TRUE, eval = TRUE}
##fitt <- coxph(Surv(enter, exit, event) ~ hisclass * period * sex + civst + urban, data = vb1)
source("R/makeTab.R")
vb1Tab <- makeTab(vb1)
source("~/R/Testing/pch.R")
Tfit <- pch(event ~ offset(log(exposure)) + age + hisclass * period * sex + civst + urban, seq(40, 65, by = 5), vb1Tab)
Tdr <- drop1(Tfit, test = "Chisq")
knitr::kable(Tdr, caption = "ANOVA, ages 40-65.")
# vb3064$social_class <- vb3064$hisclass
# vb3064$marital_status <- vb3064$civst
# vb3064$urban_or_rural <- vb3064$urban
# vb3064$age_group <- vb3064$age
# fitt <- glm(event ~ offset(log(exposure)) + urban_or_rural + marital_status + age_group + sex * social_class * period,
#             data = vb3064, family = poisson)
##dr <- drop1(fitt, test = "Chisq")
# ##dr
##knitr::kable(dr, caption = "Single term deletions, ages 30-64.")
# ##print(xtable(dr,label = "tab:cumswtab", caption = "Mortality: ANOVA, ages 30--64."),
  ##    type = "latex", comment = FALSE)
```
